% Document class and font size
\documentclass[a4paper,9pt]{extarticle}

% Packages
\usepackage[utf8]{inputenc} % For input encoding
\usepackage{geometry} % For page margins
\geometry{letterpaper, margin=0.75in} % Set paper size and margins
\usepackage{titlesec} % For section title formatting
\usepackage{enumitem} % For itemized list formatting
\usepackage{hyperref} % For hyperlinks
\usepackage{tabularx}
\usepackage{fancyhdr}

% Formatting
\setlist{noitemsep} % Removes item separation
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule] % Section title format
\titlespacing*{\section}{0pt}{\baselineskip}{\baselineskip} % Section title spacing
%%%%%%%%%%

% Begin document
\begin{document}

% Disable page numbers
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhead{}
\fancyhead[L]{\textit{Zonghui Mai}}
\fancyhead[R]{\textit{\# month \#year}}
\thispagestyle{empty} % Remove header from the first page

% Header
\begin{flushleft}
\textbf{\LARGE Zonghui Mai}\\[2pt] % Name
undergraduate student, Shantou University, Shantou, China
\\ \href{mailto:zhmai@stu.edu.cn}{zhmai@stu.edu.cn} | \href{tel:8615622255383}{+86 15622255383} | \href{https://zonghuimai.github.io}{personal homepage} 
\end{flushleft}

% Education Section
\section*{RESEARCH INTERESTS}
\noindent
Physical enhancement, Constitutive model, Multimodality, Affective Computing
% Education Section
\section*{EDUCATION}
\noindent
\textbf{Shantou University}, Shantou, China \hfill Sep 2023 | Present\\ % University name and location
bachelor in Data Science and Big Data Technology  \hfill Cumulative GPA: 3.89/5.00 \\ % Degree and GPA
\textit{Selected Courses:} Data Structure and Algorithm; Operating System; Database Theory; Object-Oriented Programming; C Language Programming; Python Programming Practice; Programming Design Foundation; Basic Software Design; System Design and Integration I; Machine Learning; Statistical Learning Method; Data Visualization; Data Collecting Techniques; Multi-source Information Fusion; Calculus B-I; Calculus B-II; Advance Calculus; Linear Algebra (Engineering); Probability and Statistics; Discrete Mathematics.\\

\noindent\\
\textbf{University of Cambridge},  Cambridge, UK \hfill 21 Jul 2024 | 3 Aug 2024\\ % University name and location
Deep Learning Summer Program % Degree and GPA
% Additional info
\hfill Cumulative GPA: 3.9/4.00


% Experience Section
\section*{RESEARCH EXPERIENCE}
\noindent
\textbf{Develop Muliti-stage physical constraint framework applied in Constitutive Models} \hfill Shantou University, China\\ % Company name and location
\textit{Third Author, Mentor: Zhen Wang} \hfill Jul 2024 | Sep 2025 % Position and duratio

\begin{itemize}
    \item To address the problem of insufficient physical consistency in data-driven constitutive models, a multi-stage physical-constraint learning framework was constructed to study the embedding strategies of physical priors and their effects.
    \item Baseline models (e.g., MLP, RNN, and PINN) and a unified experimental environment were built and implemented for method comparison and ablation analysis.
    \item An evaluation dataset and experimental protocol were constructed based on material mechanics-related properties, and evaluation was conducted from the perspectives of performance, stability, and physical consistency.
    \item The first and second laws of thermodynamics were incorporated into training in the forms of data constraints and network structural constraints, respectively; a stage-wise physical-constraint mechanism was designed and its effects were verified.
    \item Responsible for writing the Method and Experiments sections of the paper, and completed key experimental design, result analysis, figure preparation, and reference organization.
    \item Responsible for periodic academic presentations, presenting the method design and experimental conclusions.
    % Job responsibilities and achievements
\end{itemize}

\noindent
\textbf{Models Communication} \hfill Shantou University, China\\ % Company name and location
\textit{Leader, Mentor: Zhen Wang} \hfill Nov 2025 | Present % Position and duratio

\begin{itemize}
    \item For multi-model collaborative learning, designed an inter-model communication protocol to explore information interaction mechanisms during training/inference.
    \item Implemented and validated the communication protocol in constitutive thermodynamics tasks; results showed that, under specific settings, smaller-parameter models can obtain performance/efficiency gains superior to complex models through communication-based collaboration.
    \item Leading the extension of the communication mechanism to medical ultrasound image segmentation tasks and verifying its cross-domain applicability.
    \item  Guiding group members in conducting application experiments of the communication protocol on different tasks.
    \item Participating in paper writing and result organization.
    % Job responsibilities and achievements
\end{itemize}

\noindent
\textbf{Multi-level Context-aware Reasoning and Multimodality for Visual Emotion Analysis} \hfill STU, China\\ % Company name and location
\textit{First Author, Mentor: Rui Li} \hfill Apr 2025 | Jan 2026 % Position and duration

\begin{itemize}
    \item For problems in VEA tasks such as dispersed emotional cues and insufficient cross-modal semantic alignment, studied multi-level context-aware reasoning and multimodal fusion methods.
    \item Compared the performance of multiple text-image fusion strategies on VEA tasks and proposed improvement schemes based on experimental results.
    \item Collected and organized commonly used VEA datasets, and completed analyses of data distribution, data volume bias, and dataset characteristics to support model design and experimental settings.
    \item Investigated representative baseline models and constructed a unified comparison benchmark to ensure comparability and reproducibility of subsequent validation.
    \item Studied the role of the text modality in VEA, constructed a textualized expression framework for image emotion by integrating knowledge from affective science/psychology, and improved emotion representation capability through multimodal modeling, achieving SOTA on multiple datasets.
    \item Responsible for paper writing, experimental result visualization, and figure plotting.
    % Job responsibilities and achievements
\end{itemize}

\noindent
\textbf{Medical Ultrasound Segmentation model and AI Agent} \hfill Shantou University, China\\ % Company name and location
\textit{Group leader, Course Project, Basic Software Design Course} \hfill Sep 2025 | Dec 2025 % Position and duratio

\begin{itemize}
    \item Participated in building an integrated medical ultrasound segmentation model + AI Agent system for segmentation and result analysis.
    \item Investigated AI Agent frameworks and medical image segmentation models, completed technical selection, and set up the training environment and experimental pipeline.
    \item Collected and preprocessed ultrasound datasets, adapted segmentation models to task requirements, and completed model service encapsulation and front-end integration for AI Agent invocation.
    % Job responsibilities and achievements
\end{itemize}

\noindent
\textbf{Deep Learning Summer Programme} \hfill Cambridge, UK\\ % Company name and location
\textit{Mentor: Pietro Lio} \hfill 21 Jul 2025 | 3 Aug 2026 % Position and duration

\begin{itemize}
    \item Studied the full architecture of Deep Reinforcement Learning (DRL) and delved into Multi-Agent Reinforcement Learning (MARL) algorithms, including DDPG (Deep Deterministic Policy Gradient) and MADDPG (Multi-Agent DDPG).
    \item Collaborated with a team of 11 members to develop a “Simple World Communicate Game” as the main project.
    \item Took responsibility for explaining the key algorithms (DDPG and MADDPG) used in the game, presenting their application and implementation to the team. And finally got 70\% grape of this program.
\end{itemize}

\section*{PUBLICATIONS}
\noindent
\textbf{Journal paper}\\
\textup{Under review}
\begin{itemize}
    \item Wang, Z., Zhang, C., \textbf{Mai, Z.}, Wang, M., Chen, X., Yi, Y., \& Chen, H. \textit{An Artificial Neural Networks Framework for Constitutive Modeling Enhanced by Multi-stage Thermodynamic Constraints}. Submitted to \textit{International Journal of Mechanical Sciences}. Manuscript Number: SUBMIT2IJMS-D-25-09869.
\end{itemize}

\noindent
\textbf{Conference paper}\\
\textup{Under review}
\begin{itemize}
    \item \textbf{Mai, Z.}, Li, R., \& Wu, S. \textit{Multi-level Context-aware Reasoning for enhancing Visual Sentiment Analysis: Decoding Image-Inherent Sentiment-Stimuli}. Submitted to \textit{IJCAI-ECAI 2026 Main Track}. Submission ID: 5266.
\end{itemize}
\section*{ENGLISH TEST \& ADDITIONAL SKILLS}
\begin{itemize}
    \item \textbf{Duolingo English Test (DET):} 110 (Overall); Literacy 110, Comprehension 115, Conversation 110, Production 85
    \item \textbf{Languages:} Mandarin (Native), Cantonese (Native), English (Fluent)
    \item \textbf{Saxophone:} Awarded First Prize in Instrumental Group A at the 7th Guangdong University Students' Art Exhibition
    \item \textbf{English Debate:} Won Second Prize at the 2024 Guangdong International Speech and Debate Championship and Shantou Intercollegiate English Debate Competition; Won Second Prize in the 5th FLTRP English Debate Novice Championship
\end{itemize}

\section*{REFERENCES}
\textbf{Zhen Wang}\\
\textit{lecturer, Department of Civil Engineering and Smart Cities, Shantou University, Shantou, China}\\
E-mail: \href{mailto:wzhen@stu.edu.cn}{wzhen@stu.edu.cn}\\
Scholar Profiles: \href{https://eng.stu.edu.cn/info/1085/2064.htm}{Shantou University- Personal Page} \\ \\
\noindent
\textbf{Rui Li}\\
\textit{lecturer, Department of Computer Science and Technology, Shantou University, Shantou, China}\\
E-mail: \href{mailto:ruili@stu.edu.cn}{ruili@stu.edu.cn}\\
Scholar Profiles: \href{https://www.stu.edu.cn/cmac/info/1451/5301.htm}{hantou University - Personal Page} | \href{https://scholar.google.com/citations?user=V9oO4oMAAAAJ&hl=en}{Google Scholar} \\ \\
\textbf{DaZhi Jiang}\\
\textit{Professor, Department of Computer Science and Technology, Shantou University, Shantou, China}\\
E-mail: \href{mailto:dzjiang@stu.edu.cn}{dzjiang@stu.edu.cn}\\
Scholar Profiles: \href{https://www.stu.edu.cn/cmac/info/1451/15891.htm}{Sh antou University - Personal Page}\\ \\
% End document
\end{document}
